\documentclass[margin, line]{res}

\usepackage[usenames, dvipsnames]{color}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{array}
\usepackage{fontspec}
% until orcid is in fontawesome
\usepackage{orcidlink}
\usepackage{fontawesome}


\pagenumbering{gobble}

\definecolor{darkcerulean}{rgb}{0.03, 0.27, 0.49}
\definecolor{cobalt}{rgb}{0.0, 0.28, 0.67}
\definecolor{blue(pigment)}{rgb}{0.2, 0.2, 0.6}
\definecolor{airforceblue}{rgb}{0.36, 0.54, 0.66}
\definecolor{coolblack}{rgb}{0.0, 0.18, 0.39}
\hypersetup{colorlinks=true, urlcolor=darkcerulean}

% Social media links
\newcommand{\so}{https://stackoverflow.com/users/2180446/gavinsdavies}
\newcommand{\li}{https://www.linkedin.com/in/gavinsdavies}
\newcommand{\gh}{https://github.com/gavinsdavies}
\newcommand{\personalsite}{https://gavinsdavies.com}
\newcommand{\medium}{https://medium.com/@gavinsdavies}
\newcommand{\orcid}{0000-0002-5728-5356}

\newcommand{\IU}{https://physics.indiana.edu/}
\newcommand{\ISU}{https://www.physastro.iastate.edu/}
\newcommand{\OleMiss}{https://physics.olemiss.edu/}
\newcommand{\Lancs}{https://www.lancaster.ac.uk/physics/}
\newcommand{\APS}{https://www.aps.org/}
\newcommand{\MSU}{https://pa.msu.edu/}

\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in

% if using pdflatex:
% \setlength{\pdfpagewidth}{\paperwidth}
% \setlength{\pdfpageheight}{\paperheight}
%
\newenvironment{list1}{
	\begin{list}{\ding{113}}{%
		\setlength{\itemsep}{0in}
		\setlength{\parsep}{0in} \setlength{\parskip}{0in}
		\setlength{\topsep}{0in} \setlength{\partopsep}{0in}
		\setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
	\begin{list}{$\bullet$}{%
		\setlength{\itemsep}{0in}
		\setlength{\parsep}{0in} \setlength{\parskip}{0in}
		\setlength{\topsep}{0in} \setlength{\partopsep}{0in}
		\setlength{\leftmargin}{0.2in}}}{\end{list}}

\begin{document}

\name{
    \vspace*{-.5in}
	{\huge Dr. Gavin S. Davies}
	\hspace*{.1in}
	{
		\href{\li}{\faLinkedin}
		\href{\gh}{\faGithub}
		\href{\so}{\faStackOverflow}
        \orcidlink{\orcid}
	}
	\vspace*{.1in}
	}

\begin{resume}
\section{\sc Contact Information}
\vspace{.05in}
\begin{tabular}{@{}p{3.17in}>{\raggedleft\arraybackslash}p{2.66in}}
	% street,
	Oxford, MS 38655 & (+1) 331-442-3845\\
    \href{mailto:gsdavies@olemiss.edu}{gsdavies@olemiss.edu}
        & \href{\personalsite}{\personalsite}\\
        % & Currently working on ...\\
	% town, zip
    % phone number
\end{tabular}

\section{\sc Background}

\begin{list2}
	\item Experimental High Energy physicist studying neutrino oscillations
\end{list2}

% \vspace{0.15in}
\section{\sc Professional Experience}

{\bf Associate Professor of Physics \& Astronomy} \hfill {July 2025 - Present}\\
\href{\OleMiss}{University of Mississippi}, {\em Dept. of Physics \& Astronomy, Oxford, MS USA}\\
{\em University of Mississippi Center for Multi-Messenger Astrophysics Affiliate}\\
\vspace{-.5cm}

{\bf Assistant Professor of Physics \& Astronomy} \hfill {Aug. 2019 - July 2025}\\
\href{\OleMiss}{University of Mississippi}, {\em Dept. of Physics \& Astronomy, Oxford, MS USA}\\
{\em University of Mississippi Center for Multi-Messenger Astrophysics Affiliate}\\
\vspace{-.5cm}

{\bf Postdoctoral Research Fellow} \hfill{Oct. 2014 - Aug. 2019}\\
\href{\IU}{Indiana University}, {\em Dept. of Physics, Bloomington, IN USA}\\
{\em Supervisor: Prof. Mark Messier}\\
\vspace{-.5cm}
%\begin{list2}
% \item something
%	\item Postdoc work
% \item 
%\end{list2}

{\bf Postdoctoral Researcher} \hfill{ Jul. 2010 - Oct. 2014}\\
\href{\ISU}{Iowa State University}, {\em Dept. of Physics, Ames, IA USA}\\
{\em Supervisor: Prof. Mayly Sanchez}\\
\vspace{-.5cm}

\section{\sc Education}
{\bf Doctor of Philosophy (Ph.D.) in Physics} \hfill {Oct. 2006 - July 2010}\\
\href{\Lancs}{Lancaster University}, {\em Dept. of Physics, Lancaster, UK}\\
{\em Dissertation:} 'Understanding and calibrating the DS-ECal of ND280 in the T2K project'\\
{\em Ph.D. Advisor: Dr. Laura Kormos}\\
\vspace{-.5cm}

{\bf M.Phys (Hons.) Physics / USA} \hfill {Oct. 2002 - July 2006}\\
\href{\Lancs}{Lancaster University}, {\em Dept. of Physics, Lancaster, UK}\\
{\em Dissertation:} 'A Study of Charge Transfer Inefficiency in a
Simulated CCD Damaged by Particle Radiation'\\
{\em USA Study Abroad Program,} \href{\MSU}{Michigan State University}{\em , MI USA} \hfill {Aug. 2004 - May 2005}\\

\section{\sc Leadership Experience}
{\bf DUNE Phlex Adoption Working Group co-lead} \hfill {May. 2026 - Present}\\
\vspace{-.3cm}

{\bf DUNE Global Software Technical Lead} \hfill {Jan. 2026 - Present}\\
\vspace{-.3cm}

{\bf EMPHATIC Software \& Analysis Coordinator} \hfill {Oct. 2022 - Present}\\
\vspace{-.3cm}

{\bf NOvA Institutional Board Chairperson} \hfill {Mar. 2021 - Mar. 2023}\\
{\em Elected position}\\
\vspace{-.3cm}

{\bf NOvA Computing Coordinator} \hfill {Jan. 2020 - Present}\\
\vspace{-.3cm}

{\bf Fermilab Users Executive Committee Chairperson} \hfill {Sep. 2018 - Sep. 2019}\\
{\em Elected position}\\
\vspace{-.3cm}

{\bf NOvA Exotic Neutrino Oscillation Analysis Convener} \hfill {Oct. 2017 - Sep. 2022}\\
\vspace{-.3cm}

{\bf NOvA Production Convener, Software Releases and Framework Manager} \hfill {Feb. 2011 - July 2014}\\

\section{\sc Committees, Service, and Awards}
{\bf APS DPF Coordinating Panel for Software \& Computing [CPSC]} \hfill {Mar. 2025 - Present}\\
{\em Panel member, Rising Star Awards Sub-Committee Lead}\\
\vspace{-.3cm}

{\bf International Conference of High Energy Physics [ICHEP24]} \hfill {July 2024}\\
{\em Computing co-chair, Prague}\\
\vspace{-.3cm}

{\bf Graduate Program Coordinator, Dept. of Physics \& Astronomy, University of Mississippi}
\hfill {Jan. 2025 - Present}\\
\vspace{-.3cm}

{\bf APS Formation Task Force for the Coordinating Panel for Software and Computing} \hfill {Dec. 2023 - July 2024}\\
\vspace{-.3cm}

{\bf APS DPF Particle Physics Planning: Topical Group convener} \hfill {Apr. 2020 - July 2023}\\
{\em End-User Analysis}\\
\vspace{-.3cm}

{\bf Department of Energy Office of Science User Facilities Roundtable} \hfill {Oct. 2020 - June 2021}\\
{\em Committee member}\\
\vspace{-.3cm}

{\bf Flavor Physics and CP Violation (FPCP) international conference} \hfill {May 2021 - May 2022}\\
{\em Organizing Committee}\\
\vspace{-.3cm}

{\bf NOvA Executive Committee} \hfill {May 2018 - Present}\\
{\em Elected position}\\
\vspace{-.3cm}

{\bf Advocacy for High-Energy Physics Funding} \hfill {2017 - Present}\\
{\em UEC Washington D.C. Trip}\\
\vspace{-.3cm}

{\bf Fermilab Users Executive Committee (UEC)} \hfill {Sep. 2017 - Sep. 2019}\\
{\em Elected position}\\
\vspace{-.3cm}

{\bf Breakthrough Prize in Fundamental Physics} \hfill {2016}\\

\section{\sc Extracurricular}
{\href{\APS}{APS}}
\vspace*{-.0in}
% List DPF etc here?? Snowmass contribs
{\em Member} \hfill { 2014 - Present} \\
\vspace*{-0.3in}

\vspace{0.2in}
%centerline{\emph{Referees Available on Request}}

\section{\sc Outreach \& Public Engagement}

{\bf UM Excellence in Community Engaged Teaching and Learning Award} \hfill {2025}\\
{\em Team member, Dept. of Physics \& Astronomy Astronomy Art Contest}\\
\vspace{-.3cm}

{\bf Mississippi Region VII Science Fair} \hfill {2025}\\
{\em Judge}\\
\vspace{-.3cm}

{\bf University of Mississippi Academic Quiz Tournament} \hfill {2020, 2021, 2023, 2024}\\
\vspace{-.3cm}

{\bf 8th Annual Mississippi FIRST Tech Challenge Robotics Championship} \hfill {Feb. 2020}\\
\vspace{-.3cm}

{\bf UM Spooky Physics} \hfill {2022 - Present}\\
{\em Annual Halloween participant (Mr. Freeze demo)}\\
\vspace{-.3cm}

{\bf Oxford Science Cafe} \hfill {2020}\\
{\em Quizmaster (during COVID-19 pandemic)}\\
\vspace{-.3cm}

{\bf Graduate Fair Informational Tables}\\
{\em Dept. of Physics \& Astronomy representative}\\
\vspace{-.3cm}

\section{\sc Grants}

{\em External Funding (Awarded); Total (awarded): \$4,576,992}

{\bf Establishing a Scientific Computing Hub at the University of Mississippi} \hfill {Sep. 2025 -- Aug. 2027}\\
{\em Principal Investigator}, U.S. Dept. of Energy (EPSCoR), Award DE-SC0026215, \$1,800,000\\
{\em Co-PIs: B. Quinn, J. Bennett (U. Mississippi), S. Tu, S. Yang (Jackson State U.)}\\
\vspace{-.3cm}

{\bf LBNF/DUNE-US Operations} \hfill {Apr. 2026 -- Mar. 2027}\\
{\em Principal Investigator}, Fermilab, Award \#734754, \$13,349\\
\vspace{-.3cm}

{\bf URA Visiting Scholars Program: EMPHATICally Preparing for DUNE} \hfill {Jun. 2026 -- Nov. 2026}\\
{\em Principal Investigator}, Universities Research Association, Award \#2026-S-24, \$17,000\\
\vspace{-.3cm}

{\bf URA Visiting Scholars Program: EMPHATICally PINNing DUNE} \hfill {Jun. 2025 -- May 2026}\\
{\em Principal Investigator}, Universities Research Association, Award \#2025-S-13, \$16,000\\
\vspace{-.3cm}

{\bf LBNF/DUNE-US Operations} \hfill {Oct. 2025 -- Mar. 2026}\\
{\em Principal Investigator}, Fermilab, \$27,143\\
\vspace{-.3cm}

{\bf Intensity Frontier Studies at the University of Mississippi} \hfill {Sep. 2023 -- Mar. 2026}\\
{\em co-Principal Investigator}, U.S. Dept. of Energy (HEP), \$1,895,000\\
{\em Co-PIs: B. Quinn, J. Bennett (U. Mississippi)}\\
\vspace{-.3cm}

{\bf Intensity Frontier Studies at the University of Mississippi} \hfill {Nov. 2020 -- Apr. 2023}\\
{\em co-Principal Investigator}, U.S. Dept. of Energy (HEP), Award DE-SC0021616, \$800,000\\
{\em Co-PI: B. Quinn (U. Mississippi)}\\
\vspace{-.3cm}

{\bf Stimulating and Supporting Interest in STEM Fields with Hands-On Masterclass Programs} \hfill {May 2025 -- Dec. 2026}\\
{\em co-Principal Investigator}, University of Mississippi Mississippi Impact Grant, Account 250223370A, \$8,500\\
{\em PI: J. Bennett (U. Mississippi)}\\
\vspace{-.3cm}

\vspace{0.1in}
{\em Travel Awards}

{\bf ORSP Travel Grant} \hfill {May 2026}\\
{\em Travel to CHEP 2026 (Bangkok, Thailand), parallel talk}, U. Mississippi ORED, \$1,200\\
\vspace{-.3cm}

{\bf ORSP Travel Grant} \hfill {Oct. 2024}\\
{\em Travel to NBI 2024 (Mito, Japan), invited talk}, U. Mississippi ORED, \$1,200\\
\vspace{-.3cm}

{\bf ORSP Travel Grant} \hfill {Jul. 2024}\\
{\em Travel to ICHEP 2024 (Prague, Czechia), computing track convenor}, U. Mississippi ORED, \$1,188\\
\vspace{-.3cm}

\section{\sc Teaching/Student Supervision}

{\bf Teaching}
\begin{list2}
	\item PHYS 211, 212 Physics for Scientists and Engineers I/II
	\item PHYS 709 Advanced Mechanics (graduate-level)
	\item Phys 503 Science Communication (graduate-level)
	\item PHYS 510 Department Colloquium
\end{list2}

{\bf Postdoctoral Researchers}
\begin{list2}
	\item Daniel Souza Correia, University of Mississippi \hfill{2026 - Present}\\
	{\em DUNE} % https://inspirehep.net/authors/2646895
	\item Jeffrey Kleykamp, University of Mississippi \hfill{2021 - Present}\\
	{\em NOvA/DUNE} % https://inspirehep.net/authors/1281759
\end{list2}

{\bf Ph.D. Students}
\begin{list2}
	\item Noah Knutson, University of Mississippi \hfill{2024 - Present}\\
	{\em EMPHATIC}
	\item Xiaoyan Huang, University of Mississippi \hfill{2023 - Present}\\
	{\em DUNE}
	\item Bishnu Acharya, University of Mississippi \hfill{2021 - Present}\\
	{\em NOvA}
	\item Andrew Dye, University of Mississippi \hfill{2021 - May 2025}\\
	{\em Ph.D. NOvA}\\
	Now postdoctoral researcher at Wichita State University
	\item Luiz Ricardo Prais, University of Mississippi \hfill{2021 - Nov. 2024}\\
	{\em Ph.D. NOvA}\\
	Now postdoctoral researcher at University of Cincinnati
\end{list2}

{\bf M.Sc. Students}
\begin{list2}
	\item Ehsan Farooq, University of Mississippi \hfill{2024 - July 2025}\\
	{\em M.Sc. Physics (DUNE)}\\
	Now pursuing Biomedical Engineering Ph.D. at University of Mississippi
	\item Devesh Bhattarai, University of Mississippi \hfill{2020 - Aug. 2023}\\
	{\em M.Sc. Physics (NOvA/DUNE)}\\
	Now pursuing Physics Ph.D. at Mississippi State University
\end{list2}

{\bf Undergraduate Students}
\begin{list2}
	\item Suyog Badal, University of Mississippi \hfill{S25 - Present}\\
	{\em NOvA, undergraduate research}
	\item Samantha Reyes, University of Mississippi \hfill{Summer 2026 - Present}\\
	{\em MicroBooNE/DUNE machine learning, undergraduate research}
	\item Chad Byrd, University of Mississippi \hfill{Summer 2026 - Present}\\
	{\em MicroBooNE/DUNE machine learning, undergraduate research}
	\item Kaylyn Beard, University of Mississippi \hfill{S23/F24}\\
	{\em NOvA, undergraduate research}\\
	Now pursuing Physics Ph.D. at University of Minnesota
\end{list2}

{\bf Pedagogical Development}
\begin{list2}
	\item ARISE@UM mentor
	\item CETL workshop, `Energizing and Motivating Students to Learn in Uncertain and Challenging Times'
	\item CETL workshop, `Top 5 Teaching Tips from Recent Pedagogical Research'
	\item Fair and Compliant Hiring Processes workshop
	\item Graduate Program Coordinator orientation
\end{list2}


\section{\sc Selected Talks}

{\bf May 2026} `NOvA Software and Computing: Evolution, Lessons, and Impact; Supporting a Decade of Physics' {\em (contributed talk)}\\
CHEP 2026, Bangkok, Thailand\\
\vspace{-.3cm}

{\bf Apr. 2026} `Ten Years of NOvA: Precision Oscillations and the Road to DUNE' {\em (invited seminar)}\\
Niels Bohr Institute, University of Copenhagen, Copenhagen, Denmark\\
\vspace{-.3cm}

{\bf Dec. 2024} `Exploring Exotic Neutrino Oscillations with the NOvA Experiment' {\em (invited plenary talk)}\\
Miami 2024, University of Miami, Fort Lauderdale, FL\\
\vspace{-.3cm}

{\bf Nov. 2024} `Long-baseline neutrino experiments: Today and tomorrow' {\em (invited parallel talk)}\\
SESAPS 2024, UNC Charlotte, North Carolina\\
\vspace{-.3cm}

{\bf Oct. 2024} `EMPHATIC' {\em (invited plenary talk)}\\
NBI 2024, Neutrino Beams and Instrumentation, Tokai, Japan\\
\vspace{-.3cm}

{\bf Oct. 2024} `Hadron production measurements at EMPHATIC' {\em (invited parallel talk)}\\
J-PARC symposium, Mito, Japan\\
\vspace{-.3cm}

{\bf Dec. 2023} `Long-baseline neutrino experiments: hoy y mañana' {\em (invited plenary talk)}\\
8th ComHEP: Colombian Meeting on High Energy Physics, Ibagué, Colombia\\
\vspace{-.3cm}

{\bf July 2022} `Measurement of Standard and Non-standard Oscillations at NOvA' {\em (invited plenary talk)}\\
XLI International Conference on High Energy Physics [ICHEP 2022], Bologna, Italy\\
\vspace{-.3cm}

{\bf Nov. 2021} `Latest oscillation results from NOvA' {\em (invited parallel talk)}\\
SESAPS 2021, Tallahassee, Florida\\
\vspace{-.3cm}

{\bf Nov. 2019} `Latest three-flavor neutrino oscillation results from NOvA' {\em (invited parallel talk)}\\
SESAPS 2019, Wrightsville Beach, North Carolina\\
\vspace{-.3cm}

{\bf Nov. 2019} `The Fermilab Users Executive Committee Model' {\em (invited parallel talk)}\\
Society for Science at User Research Facilities (SSURF) annual meeting, College Park\\
\vspace{-.3cm}

{\bf Oct. 2019} `NOvA Software Infrastructure' {\em (invited parallel talk)}\\
Inaugural Dark-matter and Neutrino Computation Explored (DANCE) workshop, Houston, TX\\
\vspace{-.3cm}

{\bf Aug. 2019} `Latest three-flavor neutrino oscillation results from NOvA' {\em (invited parallel talk)}\\
Lepton Photon 2019, Toronto, Canada\\
\vspace{-.3cm}

{\bf Mar. 2019} `NOvA and T2K: Status and Outlook' {\em (invited plenary talk)}\\
Aspen Winter Conference, Aspen, Colorado\\
\vspace{-.3cm}

{\bf Aug. 2018} `Neutrinos, antineutrinos, and deep learning on NOvA' {\em (invited seminar)}\\
G.S. Davies, Seminar talk at Wichita State University, Wichita, KS\\
\vspace{-.3cm}

{\bf Sep. 2017} `Results and Prospects from NOvA' {\em (invited plenary talk)}\\
19th International Workshop on Neutrinos from Accelerators (NuFACT 2017), Uppsala, Sweden\\
\vspace{-.3cm}

{\bf Aug. 2016} `Searches for Sterile Neutrinos with NOvA' {\em (invited parallel talk)}\\
38th International Conference on High Energy Physics (ICHEP 2016), Chicago, Illinois, USA\\
\vspace{-.3cm}

{\bf Aug. 2016} `First Results from Searches for Active to Sterile Neutrino Oscillations with NOvA' {\em (seminar)}\\
Fermilab JETP (Wine \& Cheese) Seminar\\

\section{\sc Select Publications}

{\em 106 refereed and non-refereed publications, 12,489 citations, h-index 39 (INSPIRE-HEP, April 2026)}

% Publication totals for entries listed below (update as this section changes):
% NOvA: 24
% DUNE: 26
% T2K: 3
% Other: 3

{\bf Recent Refereed Publications (2024-2026)}
\begin{list2}
\item S. Abubakar et al. (NOvA Collaboration), ``Measurement of $\pi^0$ Production in $\bar\nu_\mu$ Charged-Current Interactions in the NOvA Near Detector'', Phys. Rev. D 113, 112008 (2026)
\item S. Abubakar et al. (NOvA Collaboration), ``Ionization-based search for magnetic monopoles using the NOvA Far Detector'', Phys. Rev. D 113, 112014 (2026)
\item S. Abbaslu et al. (DUNE Collaboration), ``Identification of low-energy kaons in the ProtoDUNE-SP detector'', Phys. Rev. D 113, 052004 (2026)
\item S. Abbaslu et al. (DUNE Collaboration), ``Operation of a Modular 3D-Pixelated Liquid Argon Time-Projection Chamber in a Neutrino Beam'', Instruments 10, 18 (2026)
\item M. A. Acero et al. (NOvA Collaboration), ``Precision Measurement of Neutrino Oscillation Parameters with 10 Years of Data from the NOvA Experiment'', Phys. Rev. Lett. 136 (2026)
\item M. A. Acero et al. (NOvA Collaboration), ``Explanation of the seasonal variation of cosmic multiple muon events observed with the NOvA Near Detector'', Phys. Rev. D 113 (2026)
\item M. A. Acero et al. (NOvA Collaboration), ``Measurement of $d^2\sigma/d|q|dE_{avail}$ in charged current neutrino-nucleus interactions at $\langle E_\nu\rangle$ = 1.86 GeV using the NOvA Near Detector'', Phys. Rev. D. 111, 052009 (2025)
\item M. A. Acero et al. (NOvA Collaboration), ``Dual-Baseline Search for Active-to-Sterile Neutrino Oscillations in NOvA'', Phys. Rev. Lett. 134, 081804 (2025)
\item M. A. Acero et al. (NOvA and T2K Collaborations), ``Joint neutrino oscillation analysis from the T2K and NOvA experiments'', Nature 646, 818 (2025)
\item M. A. Acero et al. (NOvA Collaboration), ``Monte Carlo method for constructing confidence intervals with unconstrained and constrained nuisance parameters in the NOvA experiment'', JINST 20 02, T02001 (2025)
\item S. Abbaslu et al. (DUNE Collaboration), ``Spatial and temporal evaluations of the liquid argon purity in ProtoDUNE-SP'', JINST 20 09, P09008 (2025)
\item A. Abed Abud et al. (DUNE Collaboration), ``The track-length extension fitting algorithm for energy measurement of interacting particles in liquid argon TPCs and its performance with ProtoDUNE-SP data'', JINST 20 02, P02021 (2025)
\item A. Abed Abud et al. (DUNE Collaboration), ``Supernova pointing capabilities of DUNE'', Phys. Rev. D 111 9, 092006 (2025)
\item M. A. Acero et al. (NOvA Collaboration), ``Search for CP-violating Neutrino Non-Standard Interactions with the NOvA Experiment'', Phys. Rev. Lett. 133 20, 201802 (2024)
\item A. Abed Abud et al. (DUNE Collaboration), ``First Measurement of the Total Inelastic Cross-Section of Positively-Charged Kaons on Argon at Energies Between 5.0 and 7.5 GeV'', Phys. Rev. D 110 9, 092011 (2024)
\item M. A. Acero et al. (NOvA Collaboration), ``Expanding neutrino oscillation parameter measurements in NOvA using a Bayesian approach'', Phys. Rev. D 110, 012005 (2024)
\item A. Abed Abud et al. (DUNE Collaboration), ``The DUNE Far Detector Vertical Drift Technology. Technical Design Report'', JINST 19 08, T08004 (2024)
\item A. Abed Abud et al. (DUNE Collaboration), ``DUNE Phase II: scientific opportunities, detector concepts, technological solutions'', JINST 19 12, P12005 (2024)
\item A. Abed Abud et al. (DUNE Collaboration), ``Performance of a Modular Ton-Scale Pixel-Readout Liquid Argon Time Projection Chamber'', Instruments 8 3, 41 (2024)
\item A. Abed Abud et al. (DUNE Collaboration), ``Doping liquid argon with xenon in ProtoDUNE Single-Phase: effects on scintillation light'', JINST 19 08, P08005 (2024)
\end{list2}

{\bf Publications (2020-2023)}
\begin{list2}
\item M. A. Acero et al. (NOvA Collaboration), ``Measurement of the $\nu_e$-Nucleus Charged-Current Double-Differential Cross Section at $\langle E_\nu\rangle$= 2.4 GeV using NOvA'', Phys. Rev. Lett. 130 (2023) 5, 051802 (2023)
\item A. Abed Abud et al. (DUNE Collaboration), ``Impact of cross-section uncertainties on supernova neutrino spectral parameter fitting in the Deep Underground Neutrino Experiment'', Phys. Rev. D 107, 112012 (2023)
\item M. A. Acero et al. (NOvA Collaboration), ``Improved measurement of neutrino oscillation parameters by the NOvA experiment'', Phys. Rev. D 106, 032004 (2022)
\item A. Abed Abud et al. (DUNE Collaboration), ``Design, construction and operation of the ProtoDUNE-SP Liquid Argon TPC'', JINST 17 01, P01005 (2022)
\item M. A. Acero et al. (NOvA Collaboration), ``Search for Active-Sterile Antineutrino Mixing Using Neutral-Current Interactions with the NOvA Experiment'', Phys. Rev. Lett. 127, 201801 (2021)
\item B. Abi et al. (DUNE Collaboration), ``Supernova neutrino burst detection with the Deep Underground Neutrino Experiment'', Eur. Phys. J. C 81 5, 423 (2021)
\item B. Abi et al. (DUNE Collaboration), ``First results on ProtoDUNE-SP liquid argon time projection chamber performance from a beam test at the CERN Neutrino Platform'', JINST 15 12, P12004 (2020)
\item B. Abi et al. (DUNE Collaboration), ``Long-baseline neutrino oscillation physics potential of the DUNE experiment'', Eur. Phys. J. C 80 10, 978 (2020)
\item B. Abi et al. (DUNE Collaboration), ``Deep Underground Neutrino Experiment (DUNE), Far Detector Technical Design Report, Volume IV: Far Detector Single-phase Technology'', JINST 15 08, T08010 (2020)
\end{list2}

{\bf Publications (2016-2019)}
\begin{list2}
\item M. A. Acero et al. (NOvA Collaboration), ``First Measurement of Neutrino Oscillation Parameters using Neutrinos and Antineutrinos by NOvA'', Phys. Rev. Lett. 123 151803 (2019)
\item M. A. Acero et al. (NOvA Collaboration), ``New constraints on oscillation parameters from $\nu_e$ appearance and $\nu_\mu$ disappearance in the NOvA experiment'', Phys. Rev. D 98, 032012 (2018)
\item P. Adamson et al. (NOvA Collaboration), ``Search for active-sterile neutrino mixing using neutral-current interactions in NOvA'', Phys. Rev. D. 96, 072006 (2017)
\item P. Adamson et al. (NOvA Collaboration), ``Constraints on Oscillation Parameters from $\nu_e$ Appearance and $\nu_\mu$ Disappearance in NOvA'', Phys. Rev. Lett. 118, 231801 (2017)
\item P. Adamson et al. (NOvA Collaboration), ``Measurement of the neutrino mixing angle $\theta_{23}$ in NOvA'', Phys. Rev. Lett. 118, 151802 (2017)
\item P. Adamson et al. (NOvA Collaboration), ``First Measurement of Electron Neutrino Appearance in NOvA'', Phys. Rev. Lett. 116, 151806 (2016)
\item P. Adamson et al. (NOvA Collaboration), ``First Measurement of muon-neutrino disappearance in NOvA'', Phys. Rev. D 93, 051104(R) (2016)
\end{list2}

{\bf T2K Collaboration}
\begin{list2}
\item D. Allan et al. (T2K Collaboration), ``The Electromagnetic Calorimeter for the T2K Near Detector'', JINST 8 P10019 (2013)
\item K. Abe at al. (T2K Collaboration), ``First Muon-Neutrino Disappearance Study with an Off-Axis Beam'', Phys. Rev. D. 85, 031103 (2012)
\item K. Abe et al. (T2K Collaboration), ``Indication of Electron Neutrino Appearance from an Accelerator-produced Off-axis Muon Neutrino Beam'', Phys. Rev. Lett. 107, 041801 (2011)
\end{list2}

{\bf Selected Non-refereed Publications}
\begin{list2}
\item S. Abubakar et al. (NOvA Collaboration), ``Determining Neutrino Mass Ordering with NOvA and Upcoming JUNO Measurements'', arXiv:2606.14121 (2026)
\item S. Abubakar et al. (NOvA Collaboration), ``First inclusive triple-differential measurement of the muon-antineutrino charged-current cross section using the NOvA Near Detector'', arXiv:2603.06718 (2026)
\item T. K. Aarrestad et al. (HEP Community), ``Building an AI-native Research Ecosystem for Experimental Particle Physics: A Community Vision'', arXiv:2602.17582 (2026)
\item S. Abbaslu et al. (DUNE Collaboration), ``Reconstruction of atmospheric neutrinos in DUNE's horizontal-drift far-detector module'', arXiv:2601.05697 (2026)
\item S. Abbaslu et al. (DUNE Collaboration), ``Measurement of Exclusive $\pi^+$--argon Interactions Using ProtoDUNE-SP'', arXiv:2511.13462 (2025)
\item S. Abbaslu et al. (DUNE Collaboration), ``First Measurement of $\pi^+$-Ar and $p$-Ar Total Inelastic Cross Sections in the Sub-GeV Energy Regime with ProtoDUNE-SP Data'', arXiv:2511.11925 (2025)
\item A. Abed Abud et al. (DUNE Collaboration), ``European Contributions to Fermilab Accelerator Upgrades and Facilities for the DUNE Experiment'', arXiv:2503.23744 (2025)
\item A. Abed Abud et al. (DUNE Collaboration), ``DUNE Software and Computing Research and Development'', arXiv:2503.23743 (2025)
\item A. Abed Abud et al. (DUNE Collaboration), ``The DUNE Science Program'', arXiv:2503.23291 (2025)
\item A. Abed Abud et al. (DUNE Collaboration), ``The DUNE Phase II Detectors'', arXiv:2503.23293 (2025)
\item M. A. Acero et al. (NOvA Collaboration), ``Measurement of the double-differential cross section of muon-neutrino charged-current interactions with low hadronic energy in the NOvA Near Detector'', arXiv:2410.10222 (2024)
\item Abed Abud et al. (DUNE Collaboration), ``DUNE Offline Computing Conceptual Design Report'', arXiv:2210.15665 (2022)
\item V. Daniel Elvira et al., ``The Future of High Energy Physics Software and Computing'', Snowmass 2021, arXiv:2210.05822 (2022)
\item G.S. Davies, P. Onyisi, and A. Roberts, ``CompF5: End User Analysis Topical Group Report'', Snowmass 2021, arXiv:2209.14984 (2022)
\item A. Abed Abud et al. (DUNE Collaboration), ``Snowmass Neutrino Frontier: DUNE Physics Summary'', Snowmass 2021, arXiv:2203.06100 (2022)
\item B. Abi et al. (DUNE Collaboration), ``Deep Underground Neutrino Experiment (DUNE), Far Detector Technical Design Report, Volume II: DUNE Physics'', arXiv:2002.03005 (2020)
\end{list2}

\newpage

{\bf Full INSPIRE Publication List (working draft; prune as needed)}
\input{inspire_all_publications.tex}


\end{resume}
\end{document}