{\em 109 refereed and non-refereed publications, 13,090 citations, h-index 40 (INSPIRE-HEP, July 2026)}

% Publication totals for entries listed below (update as this section changes):
% NOvA: 23
% DUNE: 28
% T2K: 3
% Other: 3

{\bf Recent Refereed Publications (2024-2026)}
\begin{list2}
\item S. Abubakar et al. (NOvA Collaboration), ``Measurement of $\pi^0$ Production in $\bar\nu_\mu$ Charged-Current Interactions in the NOvA Near Detector'', Phys. Rev. D 113, 112008 (2026)
\item S. Abubakar et al. (NOvA Collaboration), ``Ionization-based search for magnetic monopoles using the NOvA Far Detector'', Phys. Rev. D 113, 112014 (2026)
\item S. Abbaslu et al. (DUNE Collaboration), ``Identification of low-energy kaons in the ProtoDUNE-SP detector'', Phys. Rev. D 113, 052004 (2026)
\item S. Abbaslu et al. (DUNE Collaboration), ``Operation of a Modular 3D-Pixelated Liquid Argon Time-Projection Chamber in a Neutrino Beam'', Instruments 10, 18 (2026)
\item M. A. Acero et al. (NOvA Collaboration), ``Precision Measurement of Neutrino Oscillation Parameters with 10 Years of Data from the NOvA Experiment'', Phys. Rev. Lett. 136 (2026)
\item M. A. Acero et al. (NOvA Collaboration), ``Explanation of the seasonal variation of cosmic multiple muon events observed with the NOvA Near Detector'', Phys. Rev. D 113 (2026)
\item M. A. Acero et al. (NOvA Collaboration), ``Measurement of $d^2\sigma/d|q|dE_{avail}$ in charged current neutrino-nucleus interactions at $\langle E_\nu\rangle$ = 1.86 GeV using the NOvA Near Detector'', Phys. Rev. D. 111, 052009 (2025)
\item M. A. Acero et al. (NOvA Collaboration), ``Dual-Baseline Search for Active-to-Sterile Neutrino Oscillations in NOvA'', Phys. Rev. Lett. 134, 081804 (2025)
\item M. A. Acero et al. (NOvA and T2K Collaborations), ``Joint neutrino oscillation analysis from the T2K and NOvA experiments'', Nature 646, 818 (2025)
\item M. A. Acero et al. (NOvA Collaboration), ``Monte Carlo method for constructing confidence intervals with unconstrained and constrained nuisance parameters in the NOvA experiment'', JINST 20 02, T02001 (2025)
\item S. Abbaslu et al. (DUNE Collaboration), ``Spatial and temporal evaluations of the liquid argon purity in ProtoDUNE-SP'', JINST 20 09, P09008 (2025)
\item A. Abed Abud et al. (DUNE Collaboration), ``The track-length extension fitting algorithm for energy measurement of interacting particles in liquid argon TPCs and its performance with ProtoDUNE-SP data'', JINST 20 02, P02021 (2025)
\item A. Abed Abud et al. (DUNE Collaboration), ``Supernova pointing capabilities of DUNE'', Phys. Rev. D 111 9, 092006 (2025)
\item M. A. Acero et al. (NOvA Collaboration), ``Search for CP-violating Neutrino Non-Standard Interactions with the NOvA Experiment'', Phys. Rev. Lett. 133 20, 201802 (2024)
\item A. Abed Abud et al. (DUNE Collaboration), ``First Measurement of the Total Inelastic Cross-Section of Positively-Charged Kaons on Argon at Energies Between 5.0 and 7.5 GeV'', Phys. Rev. D 110 9, 092011 (2024)
\item M. A. Acero et al. (NOvA Collaboration), ``Expanding neutrino oscillation parameter measurements in NOvA using a Bayesian approach'', Phys. Rev. D 110, 012005 (2024)
\item A. Abed Abud et al. (DUNE Collaboration), ``The DUNE Far Detector Vertical Drift Technology. Technical Design Report'', JINST 19 08, T08004 (2024)
\item A. Abed Abud et al. (DUNE Collaboration), ``DUNE Phase II: scientific opportunities, detector concepts, technological solutions'', JINST 19 12, P12005 (2024)
\item A. Abed Abud et al. (DUNE Collaboration), ``Performance of a Modular Ton-Scale Pixel-Readout Liquid Argon Time Projection Chamber'', Instruments 8 3, 41 (2024)
\item A. Abed Abud et al. (DUNE Collaboration), ``Doping liquid argon with xenon in ProtoDUNE Single-Phase: effects on scintillation light'', JINST 19 08, P08005 (2024)
\end{list2}

{\bf Publications (2020-2023)}
\begin{list2}
\item M. A. Acero et al. (NOvA Collaboration), ``Measurement of the $\nu_e$-Nucleus Charged-Current Double-Differential Cross Section at $\langle E_\nu\rangle$= 2.4 GeV using NOvA'', Phys. Rev. Lett. 130 (2023) 5, 051802 (2023)
\item A. Abed Abud et al. (DUNE Collaboration), ``Impact of cross-section uncertainties on supernova neutrino spectral parameter fitting in the Deep Underground Neutrino Experiment'', Phys. Rev. D 107, 112012 (2023)
\item M. A. Acero et al. (NOvA Collaboration), ``Improved measurement of neutrino oscillation parameters by the NOvA experiment'', Phys. Rev. D 106, 032004 (2022)
\item A. Abed Abud et al. (DUNE Collaboration), ``Design, construction and operation of the ProtoDUNE-SP Liquid Argon TPC'', JINST 17 01, P01005 (2022)
\item M. A. Acero et al. (NOvA Collaboration), ``Search for Active-Sterile Antineutrino Mixing Using Neutral-Current Interactions with the NOvA Experiment'', Phys. Rev. Lett. 127, 201801 (2021)
\item B. Abi et al. (DUNE Collaboration), ``Supernova neutrino burst detection with the Deep Underground Neutrino Experiment'', Eur. Phys. J. C 81 5, 423 (2021)
\item B. Abi et al. (DUNE Collaboration), ``First results on ProtoDUNE-SP liquid argon time projection chamber performance from a beam test at the CERN Neutrino Platform'', JINST 15 12, P12004 (2020)
\item B. Abi et al. (DUNE Collaboration), ``Long-baseline neutrino oscillation physics potential of the DUNE experiment'', Eur. Phys. J. C 80 10, 978 (2020)
\item B. Abi et al. (DUNE Collaboration), ``Deep Underground Neutrino Experiment (DUNE), Far Detector Technical Design Report, Volume IV: Far Detector Single-phase Technology'', JINST 15 08, T08010 (2020)
\end{list2}

{\bf Publications (2016-2019)}
\begin{list2}
\item M. A. Acero et al. (NOvA Collaboration), ``First Measurement of Neutrino Oscillation Parameters using Neutrinos and Antineutrinos by NOvA'', Phys. Rev. Lett. 123 151803 (2019)
\item M. A. Acero et al. (NOvA Collaboration), ``New constraints on oscillation parameters from $\nu_e$ appearance and $\nu_\mu$ disappearance in the NOvA experiment'', Phys. Rev. D 98, 032012 (2018)
\item P. Adamson et al. (NOvA Collaboration), ``Search for active-sterile neutrino mixing using neutral-current interactions in NOvA'', Phys. Rev. D. 96, 072006 (2017)
\item P. Adamson et al. (NOvA Collaboration), ``Constraints on Oscillation Parameters from $\nu_e$ Appearance and $\nu_\mu$ Disappearance in NOvA'', Phys. Rev. Lett. 118, 231801 (2017)
\item P. Adamson et al. (NOvA Collaboration), ``Measurement of the neutrino mixing angle $\theta_{23}$ in NOvA'', Phys. Rev. Lett. 118, 151802 (2017)
\item P. Adamson et al. (NOvA Collaboration), ``First Measurement of Electron Neutrino Appearance in NOvA'', Phys. Rev. Lett. 116, 151806 (2016)
\item P. Adamson et al. (NOvA Collaboration), ``First Measurement of muon-neutrino disappearance in NOvA'', Phys. Rev. D 93, 051104(R) (2016)
\end{list2}

{\bf T2K Collaboration}
\begin{list2}
\item D. Allan et al. (T2K Collaboration), ``The Electromagnetic Calorimeter for the T2K Near Detector'', JINST 8 P10019 (2013)
\item K. Abe at al. (T2K Collaboration), ``First Muon-Neutrino Disappearance Study with an Off-Axis Beam'', Phys. Rev. D. 85, 031103 (2012)
\item K. Abe et al. (T2K Collaboration), ``Indication of Electron Neutrino Appearance from an Accelerator-produced Off-axis Muon Neutrino Beam'', Phys. Rev. Lett. 107, 041801 (2011)
\end{list2}

{\bf Selected Non-refereed Publications}
\begin{list2}
\item S. Abbaslu et al. (DUNE Collaboration), ``Operation and performance of ProtoDUNE Dual Phase liquid argon time projection chamber'', arXiv:2607.15927 (2026)
\item S. Abubakar et al. (NOvA Collaboration), ``Determining Neutrino Mass Ordering with NOvA and Upcoming JUNO Measurements'', arXiv:2606.14121 (2026)
\item S. Abbaslu et al. (DUNE Collaboration), ``Design of the DUNE horizontal drift far detector charge readout electronics and performance in ProtoDUNE-HD'', arXiv:2604.23966 (2026)
\item S. Abubakar et al. (NOvA Collaboration), ``First inclusive triple-differential measurement of the muon-antineutrino charged-current cross section using the NOvA Near Detector'', arXiv:2603.06718 (2026)
\item T. K. Aarrestad et al. (HEP Community), ``Building an AI-native Research Ecosystem for Experimental Particle Physics: A Community Vision'', arXiv:2602.17582 (2026)
\item S. Abbaslu et al. (DUNE Collaboration), ``Reconstruction of atmospheric neutrinos in DUNE's horizontal-drift far-detector module'', arXiv:2601.05697 (2026)
\item S. Abbaslu et al. (DUNE Collaboration), ``Measurement of Exclusive $\pi^+$--argon Interactions Using ProtoDUNE-SP'', arXiv:2511.13462 (2025)
\item S. Abbaslu et al. (DUNE Collaboration), ``First Measurement of $\pi^+$-Ar and $p$-Ar Total Inelastic Cross Sections in the Sub-GeV Energy Regime with ProtoDUNE-SP Data'', arXiv:2511.11925 (2025)
\item A. Abed Abud et al. (DUNE Collaboration), ``European Contributions to Fermilab Accelerator Upgrades and Facilities for the DUNE Experiment'', arXiv:2503.23744 (2025)
\item A. Abed Abud et al. (DUNE Collaboration), ``DUNE Software and Computing Research and Development'', arXiv:2503.23743 (2025)
\item A. Abed Abud et al. (DUNE Collaboration), ``The DUNE Science Program'', arXiv:2503.23291 (2025)
\item A. Abed Abud et al. (DUNE Collaboration), ``The DUNE Phase II Detectors'', arXiv:2503.23293 (2025)
\item M. A. Acero et al. (NOvA Collaboration), ``Measurement of the double-differential cross section of muon-neutrino charged-current interactions with low hadronic energy in the NOvA Near Detector'', arXiv:2410.10222 (2024)
\item Abed Abud et al. (DUNE Collaboration), ``DUNE Offline Computing Conceptual Design Report'', arXiv:2210.15665 (2022)
\item V. Daniel Elvira et al., ``The Future of High Energy Physics Software and Computing'', Snowmass 2021, arXiv:2210.05822 (2022)
\item G.S. Davies, P. Onyisi, and A. Roberts, ``CompF5: End User Analysis Topical Group Report'', Snowmass 2021, arXiv:2209.14984 (2022)
\item A. Abed Abud et al. (DUNE Collaboration), ``Snowmass Neutrino Frontier: DUNE Physics Summary'', Snowmass 2021, arXiv:2203.06100 (2022)
\item B. Abi et al. (DUNE Collaboration), ``Deep Underground Neutrino Experiment (DUNE), Far Detector Technical Design Report, Volume II: DUNE Physics'', arXiv:2002.03005 (2020)
\end{list2}
